---
title: "Symbolic Computation"
author: "Cea"
date: "8/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(reticulate)
# Use other python
# use_python("/home/sebastian/.pyenv/shims/python")
# Check python config
# py_config()
# Command line python
# repl_python()
# Verify conda environments
# conda_list()
# indicate that we want to use a specific condaenv
# use_condaenv("r-reticulate")
# Install package in default conda environment "r-reticulate"
# py_install("pandas")
# py_install("time")
# py_install("matplotlib")
# Unable to install the following
# py_install("math")
# py_install("sympy")
# Install package in specific environment "environment-name"
# virtualenv_install("environment-name", "scipy")
# Problem: 
# QStandardPaths: XDG_RUNTIME_DIR not set, defaulting to '/tmp/runtime-sebastian'
# No protocol specified
# qt.qpa.screen: QXcbConnection: Could not connect to display :0
# Could not connect to any X display.
# Solution found on https://community.rstudio.com/t/how-to-display-the-plot-in-the-python-chunk/22039/2
matplotlib <- import("matplotlib")
matplotlib$use("Agg", force = TRUE)

```


## Lo Esencial

```{python}
from sympy import *
x, y = symbols('x y')
expr = x + 2*y
x*(expr + 1 - x) 
# Expandimos la expresión anterior
expand(x*(expr + 1 - x) )
# Factorizamos una nueva expresión
factor(x**2+2*x*y)
```

## Operaciones simbólica

```{python}
# This will make all further examples pretty print with unicode characters.
init_printing(use_unicode=True)

x, t, z, nu = symbols('x t z nu')
```

### Derivadas

```{python}
diff(sin(x)*exp(x), x)
```

### Integrales

Vamos a integrar \(e^x\cdot\sin (x)+e^x\cdot\cos(x)\)


```{python}
expr=integrate(exp(x)*sin(x) + exp(x)*cos(x), x)
latex(expr)
```
Falta usar expresión en latex fuera del bloque de código


```{python}
integrate(sin(x**2), (x, -oo, oo))
```

### Límites

```{python}
limit(sin(x)/x, x, 0)
```

### Resuelve sistemas

```{python}
solve(x**2 - 2, x)
```

### Resuelve ecuación diferencial

```{python}
y = Function('y')
dsolve(Eq(y(t).diff(t, t) - y(t), exp(t)), y(t))
```

## Matrices

https://docs.sympy.org/latest/tutorial/matrices.html

### Valores propios matriz

```{python}
M = Matrix([[3, -2,  4, -2], [5,  3, -3, -2], [5, -2,  2, -2], [5, -2, -3,  3]])
M.eigenvals()
```
### Vectores propios

```{python}
M.eigenvects()
```

### Polinomio característico

```{python}
lamda = symbols('lamda')
p = M.charpoly(lamda)
factor(p.as_expr())
```

### Nullspace

```{python}
M = Matrix([[1-x, 2, 3, 0, 0], [4, 10, 0, 0, 1]])
M
M.nullspace()
# Primera coordenada
M.nullspace()[0]
# M*M.nullspace()[1]
# M*M.nullspace()[2]
```

Verificamos que la tercera coordenada genera el vector cero

```{r}
expr=M*M.nullspace()[0]
expr
expr.subs(x,-1)
```

